Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-01-13 ms.rmd
Clarifying acclimation time in methods

---
title: "Double trouble: Terrestrial ectortherm populations have both reduced opportunity for selection and physiological plasticity"
bibliography: ./bib/refs.bib
csl: ./bib/ecology-letters.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: ./bib/template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---

@@

    # Traits 
      traits_habitat <- data_long2 %>%
                      group_by(habitat, trait_category) %>%
                      summarise(spp_n = length(unique(species_full)), k = n())
      traits_all <- data_long2 %>%
                      group_by(trait_category) %>%
                      summarise(spp_n = length(unique(species_full)), k = n())
#########################
## Phylogeny
#########################
 ## Tree data
    tree_data <-  data_long %>%
                  group_by(species_full)                                                 %>%
                  mutate(n = length(habitat))                                            %>%
                  dplyr::select(species_full,  habitat, n)                               %>% 
                  distinct(species_full, habitat, n)
    #rownames(tree_data) <- tree_data$species_full
    #tree_data <- tree_data[,2:3]

@@

#### *Comparing variance physiological rates*
 @nakagawa2015meta recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*). *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups. We refer readers to @nakagawa2015meta for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:

@@

To understand how climate has impacted species’ physiological acclimation abilities we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments. It was unclear whether climate at the locations of captive reared organisms would be representative of a populations climate history - particularly for species reared under captive condition for many generations. Given that we were interested in understanding climate driven effects on acclimation capacity we only used studies on wild populations were used for climate analyses.

@@

### *Meta-Analysis*
We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers. `r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers. `r utils::packageVersion("brms")` @Burkner2018; @Burkner2017; @stan] and *metafor* [vers. `r utils::packageVersion("metafor")` @Viechtbauer2010].  We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers. 2.0, @Nakagawa2021c]. In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021; @Song2021]. For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution. We used flat Gaussian priors for 'fixed' effects (i.e., $N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$). We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$).

@@

#### *Multi-level Meta-regression (MLMR) Models*
We controlled for the duration of time organisms were given to acclimate by included scaled acclimation time (mean = 0, SD = 1) in all models.

@@

The final dataset included a total of `r f <- taxa_sum %>% filter(habitat == "f") %>% summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum %>% filter(habitat == "f" & class == "Actinopterygii") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "f" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Amphibians = `r taxa_sum %>% filter(habitat == "f" & class == "Amphibia") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "f" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "f" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum %>% filter(habitat == "m") %>% summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum %>% filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) %>% summarise(sp = sum(spp))`, Annelids = `r taxa_sum %>% filter(habitat == "m" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "m" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum %>% filter(habitat == "m" & phylum == "Echinodermata") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "m" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "m" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single species of Crustacean, Cnidarian), and `r t <- taxa_sum %>% filter(habitat == "t") %>% summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum %>% filter(habitat == "t" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "t" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "t" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "t" & class == "Reptilia") %>% summarise(sp = sum(spp))` and Amphibians = `r taxa_sum %>% filter(habitat == "t" & class == "Amphibia") %>% summarise(sp = sum(spp))` along with a single Tardigrade species) (Fig. \@ref(fig:fig1)A). We had more data on acute thermal responses (n = `r trimmed <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acclim"); sum2$n`) (Fig. \@ref(fig:fig1)A).

@@

  # Check whether there is differences in variances for each habitat
  model1.2_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 + type + habitat | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data)

@@

   # Prune tree
   tree_m <- tree_checks(lnRRQ10_data_m, tree = tree_lnrr, dataCol = "species_full", type = "prune")
   tree_f <- tree_checks(lnRRQ10_data_f, tree = tree_lnrr, dataCol = "species_full", type = "prune")
   tree_t <- tree_checks(lnRRQ10_data_t, tree = tree_lnrr, dataCol = "species_full", type = "prune")

@@

if(rerun){
   # More realistic model with traits in marine species. Remove antioxidants because there are just too few effects
  # Filter out antioxidant
  lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox" | !is.na(effect_size))

  model1.3_m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 | obs),
                              R = list(species_full = m_phylo), dfs = "contain", 
                              test = "t", 
                              data = lnRRQ10_data_m)

  model1.3_m_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 + trait_category | obs),
                              R = list(species_full = m_phylo), 
                              str = "HCS", rho = 0, dfs = "contain", 
                              test = "t", data = lnRRQ10_data_m)

  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", data = lnRRQ10_data_m, angle = 45)

  # Cannot model heterogeneous variance across traits if use sigma + TRUE, so just use obs.
   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) +(1|trait) + (1 + type + trait_category + type:trait_category|gr(obs, cor = FALSE)),  data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)

@@

   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)

@@

@@

  # Save models
  saveRDS(model1.3_m, file = "./output/models/lnRRQ10_1.3m")
  saveRDS(model1.3_m_het, file = "./output/models/lnRRQ10_1.3m_het")
  saveRDS(model1.3_m_bayes, file = "./output/models/lnRRQ10_1.3_bayes_m")
  saveRDS(model1.3_f, file = "./output/models/lnRRQ10_1.3f")
  saveRDS(model1.3_f_bayes, file = "./output/models/lnRRQ10_1.3_bayes_f")
  saveRDS(model1.3_t, file = "./output/models/lnRRQ10_1.3t")
  saveRDS(model1.3_t_bayes, file = "./output/models/lnRRQ10_1.3_bayes_t")

@@

```{r, fig1, fig.align='center', fig.cap= "**Phylogeny and Q10 estimate for acute and acclimation type effects**. A) Phylogenetic distribution of taxa contained within the data. Total number of acute and acclimation type Q10 effect sizes are highlighted as well as if the taxa is marine, freshwater or terrestrial. Silouettes are representative taxa of major clades within the tree. B) Acute and Acclimation lnRR Q10 across marine, freshwater and terrestrial environments. C) lnCVR Q10 across traits for marine, freshwater and terrestrial systems. Note there were no differences between acute and acclimation Q10 types. k = total number of effect size estimates while numbers in brackets indicate the number of species."}

@@

## References

## Extra Figures

>>>>

---
title: "Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change"
bibliography: ./bib/refs.bib
csl: ./bib/ecology-letters.csl
output: 
  bookdown::word_document2:
    toc: no
    toc_depth: 6
    number_sections: false
    reference_docx: ./bib/template.docx
  bookdown::html_document2:
    code_folding: hide
    number_sections: no
    toc: yes
    toc_depth: 6
    toc_float: yes
    bibliography: refs.bib
editor_options: 
  chunk_output_type: console
---

@@

    # Traits 
      traits_habitat <- data_long2 %>%
                      group_by(habitat, trait_category) %>%
                      summarise(spp_n = length(unique(species_full)), k = n())
      traits_all <- data_long2 %>%
                      group_by(trait_category) %>%
                      summarise(spp_n = length(unique(species_full)), k = n())
    # Acclimation time vary across habitat?

      acclim_time <- data_wide %>% 
                      group_by(habitat) %>% 
                      summarise(mean = mean(acclim_period, na.rm = TRUE),
                                  sd = sd(acclim_period, na.rm = TRUE),
                                  n = n())
      test_m_t <- t.test(acclim_period ~ habitat, data = data_wide %>% filter(!habitat == "f"))
      test_f_t <- t.test(acclim_period ~ habitat, data = data_wide %>% filter(!habitat == "m"))
      test_f_m <- t.test(acclim_period ~ habitat, data = data_wide %>% filter(!habitat == "t"))

#########################
## Phylogeny
#########################
 ## Tree data
    tree_data <-  data_long %>%
                  group_by(species_full)                                                 %>%
                  mutate(n = length(habitat))                                            %>%
                  dplyr::select(species_full,  habitat, n)                               %>% 
                  distinct(species_full, habitat, n)
    #rownames(tree_data) <- tree_data$species_full
    #tree_data <- tree_data[,2:3]

@@

#### *Comparing variance in physiological rates*
 @nakagawa2015meta recently proposed analogous effect size estimates to *lnRR* that allow for comparisons of changes in variance between two groups, the log variance ratio (*lnVR*) and the log coefficient of variation (*lnCVR*). *lnVR* and *lnCVR* are ratios that describe the relative difference in trait variability between two groups. We refer readers to @nakagawa2015meta for the equations describing *lnVR* and *lnCVR*, but these can easily be extended to their $Q_{10}$ analogues (and associated sampling variance) as follows:

@@

To understand how climate has impacted species’ physiological acclimation abilities we used the coordinates reported by each study to extract temperature data from terrestrial and aquatic environments. It was unclear whether climate at the locations of captive reared organisms would be representative of a population's climate history - particularly for species reared under captive condition for many generations. Given that we were interested in understanding climate driven effects on acclimation capacity we only used studies on wild populations were used for climate analyses.

@@

### *Meta-Analysis*
We analysed our data using multilevel meta-analytic (MLMA) and meta-regression (MLMR) models in R (vers. `r paste0(R.Version()$major, ".", R.Version()$minor)`) using *brms* [vers. `r utils::packageVersion("brms")` @Burkner2018; @Burkner2017; @stan] and *metafor* [vers. `r utils::packageVersion("metafor")` @Viechtbauer2010].  We fit both Bayesian and frequentist approaches to ensure that our results were consistent, and to create orchard plots more easily [vers. 2.0, @Nakagawa2021c]. In addition, Bayesian methods better protect against type I errors in the presence of complex sources of non-independence [@Nakagawa2021; @Song2021]. For our Bayesian models, we ran 4 MCMC chains, each with a warm-up of 1000 followed by 4000 sampling iterations keeping every 5 iterations for a total of 3200 samples from the posterior distribution. We used flat Gaussian priors for 'fixed' effects (i.e., $N(0, 10)$) and a student t-distribution for 'random' effects (i.e., $student_{t}(3, 0, 10)$). We checked that all MCMC chains were mixing and had converged (i.e., $R_{hat} = 1$). We compared any competing models using Akaike's Information Criteria (AIC) (if frequentist) or Wantabe Information Criteria (WIC) (if Bayesian). We deemed models with the lowest IC value to be best supported if there was a $\Delta IC$ between the competing models of 2 or more. If two models were within 2 $\Delta IC$ units we went with the most parsimonious model.

@@

#### *Multi-level Meta-regression (MLMR) Models*

After quantifying levels of heterogeneity, we fit a series of multi-level meta-regression (MLMR) models to test our key questions. In all models, we included the same random effects as we used in our MLMA models. Acclimation time varied from `r range(data_wide$acclim_period, na.rm = TRUE)[1]` to `r range(data_wide$acclim_period, na.rm = TRUE)[2]` days (mean (SD) = `r mean(data_wide$acclim_period, na.rm = TRUE)` $\pm$ `r sd(data_wide$acclim_period, na.rm = TRUE)` days), and terrestrial ectotherms were acclimated for a much shorter duration (mean (SD) = `r acclim_time[3,2]` $\pm$ `r acclim_time[3,3]`, n = `r acclim_time[3,4]`) than both freshwater (mean (SD) = `r acclim_time[1,2]` $\pm$ `r acclim_time[1,3]`, n = `r acclim_time[1,4]`) and marine species (mean (SD) = `r acclim_time[2,2]` $\pm$ `r acclim_time[2,3]`, n = `r acclim_time[2,4]`). Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023], which would make it more likely that terrestrial ectotherms would show lower post acclimation $lnRR_{Q_{10}}$. Nonetheless, acclimation time was mean-centered (mean = 0) and controlled for in all our models. As such, all estimates can be interpreted as values for an average level of acclimation time (i.e., `r mean(data_wide$acclim_period, na.rm = TRUE)` days).

We first tested the degree to which acute and acclimation $lnRR_{Q_{10}}$ and $lnCVR_{Q_{10}}$ effects varied by habitat type (i.e., terrestrial, freshwater, and marine ecosystems). Models included an interaction between effect type (i.e., acute or acclimation) and habitat. Reduced mean $lnRR_{Q_{10}}_{acclimation}$ relative to $lnRR_{Q_{10}}_{acute}$ indicates that acclimation to thermal environments results in partial compensation of physiological rates (i.e., phenotypic plasticity), whereas no differences between $lnRR_{Q_{10}}_{acute}$ and $lnRR_{Q_{10}}_{acclimation}$ suggests organisms are not capable of physiological plasticity [@Havird2020]. In contrast, a difference in $lnCVR_{Q_{10}}_{acclimation}$ relative to $lnCVR_{Q_{10}}_{acute}$ would imply that changes in between individual variation in physiological rates across 10$^{\circ}$C differ depending on whether acute or acclimation responses are measured. If the interaction between effect type and habitat was not supported, then we fit a model that only contained additive effects of effect type and habitat. Following on from these models, we subset each habitat type and explored how mean $lnRR_{Q_{10}}$ changed across traits. Within each habitat (marine, freshwater, and terrestrial) we fit a series of models that included an interaction between effect type (acute / acclimation) and trait category (as defined above). Variance in effects within trait categories appeared to vary depending on the trait type in question. Comparison of a model with and without heteroscedastic residual variance favored a model with heteroscedastic residual variance across trait categories ($\Delta AIC_{c}$; marine = 58, freshwater = ,  and terrestrial = )

Second, we tested whether different life-stages are more or less likely to acclimate by fitting a model for each habitat type and including an interaction between life-stage ('adult' or 'juvenile') and effect type. We predicted that acclimation responses maybe more likely early in development compared to later in development, but that this should depend on the habitat type given the different constraints faced by different early life stages across major habitat types.

@@

The final dataset included a total of `r f <- taxa_sum %>% filter(habitat == "f") %>% summarise(spp = sum(spp), k = sum(n)); f[1,1]` freshwater (fishes = `r taxa_sum %>% filter(habitat == "f" & class == "Actinopterygii") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "f" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Amphibians = `r taxa_sum %>% filter(habitat == "f" & class == "Amphibia") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "f" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "f" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single Crustacean and Nematode species), `r m <- taxa_sum %>% filter(habitat == "m") %>% summarise(spp = sum(spp), k = sum(n)); m[1,1]` marine (fishes = `r taxa_sum %>% filter(habitat == "m" & class %in% c("Actinopterygii", "Agnatha","Chondrichthyes")) %>% summarise(sp = sum(spp))`, Annelids = `r taxa_sum %>% filter(habitat == "m" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "m" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Echinoderms = `r taxa_sum %>% filter(habitat == "m" & phylum == "Echinodermata") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "m" & class == "Reptilia") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "m" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, and a single Crustacean and Cnidarian species), and `r t <- taxa_sum %>% filter(habitat == "t") %>% summarise(spp = sum(spp), k = sum(n)); t[1,1]` terrestrial species (Annelids = `r taxa_sum %>% filter(habitat == "t" & phylum == "Annelida") %>% summarise(sp = sum(spp))`, Molluscs = `r taxa_sum %>% filter(habitat == "t" & phylum == "Mollusca") %>% summarise(sp = sum(spp))`, Arthropods = `r taxa_sum %>% filter(habitat == "t" & phylum == "Arthropoda") %>% summarise(sp = sum(spp))`, Reptiles = `r taxa_sum %>% filter(habitat == "t" & class == "Reptilia") %>% summarise(sp = sum(spp))` and Amphibians = `r taxa_sum %>% filter(habitat == "t" & class == "Amphibia") %>% summarise(sp = sum(spp))` along with a single Tardigrade species) (Fig. \@ref(fig:fig1)A). We had more data on acute thermal responses (n = `r trimmed <- data_long2 %>% filter(grepl("lnRR", name) & !is.na(effect_size) & !is.na(V) & !V == 0); sum1 = trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acute"); sum(sum1$n)`) compared to thermal responses after an acclimation period (n = `r sum2 <- trimmed %>% group_by(name, type) %>% summarise(n = n()) %>% filter(type =="acclim"); sum2$n`) because both acclimation temperatures had separate acute responses (Fig. \@ref(fig:fig1)A).

@@

  # Check whether there is differences in variances for each habitat
  model1.2_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 + habitat | obs),
                              R = list(species_full = phylo_cor), struct = "HCS", rho = 0, dfs = "contain", 
                              test = "t", data = lnRRQ10_data)

@@

    # Filter out antioxidant
  lnRRQ10_data_m <- lnRRQ10_data_m %>% filter(!trait_category =="antiox") %>% filter(!is.na(c_accl_time))
  lnRRQ10_data_f <- lnRRQ10_data_f %>% filter(!is.na(c_accl_time))
   # Prune tree
   tree_m <- tree_checks(lnRRQ10_data_m, tree = tree_lnrr, dataCol = "species_full", type = "prune")
   tree_f <- tree_checks(lnRRQ10_data_f, tree = tree_lnrr, dataCol = "species_full", type = "prune")
   tree_t <- tree_checks(lnRRQ10_data_t, tree = tree_lnrr, dataCol = "species_full", type = "prune")

@@

if(rerun){
   # More realistic model with traits in marine species. Remove antioxidants because there are just too few effects
   model1.3_m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 | obs),
                              R = list(species_full = m_phylo), dfs = "contain", 
                              test = "t", 
                              data = lnRRQ10_data_m)

  model1.3_m_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 + trait_category | obs),
                              R = list(species_full = m_phylo), 
                              struct = "HCS", rho = 0, dfs = "contain", 
                              test = "t", data = lnRRQ10_data_m)

  # Check k is the same for both models (yes) and check which model is best supported
    AICc1.3_m     <- AIC(model1.3_m) + AICc_correction(model1.3_m)
    AICc1.3_m_het <- AIC(model1.3_m_het) + AICc_correction(model1.3_m_het)
    # Clear support for this model. We'll go with this.
    AICc1.3_m - AICc1.3_m_het

  orchard_plot(model1.3_m_het, mod = "trait_category", at = list(type = c("acclim", "acute")), by = "type", xlab = TeX("$lnRR_{Q_{10}}$"), group = "spp", data = lnRRQ10_data_m, angle = 0)

  # Cannot model heterogeneous variance across traits if use sigma + TRUE, so just use obs.
   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) +(1|trait) + (1 + trait_category |gr(obs, cor = FALSE)),  data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_m)

@@

  # Heteroscedastic variance model for freshwater
  model1.3_f_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 + trait_category | obs),
                              R = list(species_full =f_phylo), struct = "HCS", rho = 0, dfs = "contain", 
                              test = "t", data = lnRRQ10_data_f)

  ## Check support for two models
  AIC(model1.3_f_het, model1.3_f)

  # Run the Bayesian equivalent of the top supported model. 
   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V), sigma = TRUE) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 8, data = lnRRQ10_data_f)

@@

  # Heteroscedastic variance model for terrestrial
  model1.3_t_het <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 + trait_category | obs),
                              R = list(species_full =t_phylo), struct = "HCS", rho = 0, dfs = "contain", 
                              test = "t", data = lnRRQ10_data_t)

@@

  # Save models
  saveRDS(model1.3_m, file = "./output/models/lnRRQ10_1.3m")
  saveRDS(model1.3_m_het, file = "./output/models/lnRRQ10_1.3m_het")
  saveRDS(model1.3_m_bayes, file = "./output/models/lnRRQ10_1.3_bayes_m")

  saveRDS(model1.3_f, file = "./output/models/lnRRQ10_1.3f")
  saveRDS(model1.3_f_bayes, file = "./output/models/lnRRQ10_1.3_bayes_f")

  saveRDS(model1.3_t, file = "./output/models/lnRRQ10_1.3t")
  saveRDS(model1.3_t_bayes, file = "./output/models/lnRRQ10_1.3_bayes_t")

@@

```{r, fig1, fig.align='center', fig.cap= "**Taxonomic distribution of acute and acclimation Q10 estimates across major habitats**. **A)** Phylogenetic distribution of taxa contained within the data. The total number of acute and acclimation type Q10 effect sizes are highlighted as well as whether the taxa is marine, freshwater or terrestrial. Silouettes are representative taxa of major clades within the tree. **B)** Acute and Acclimation lnRR Q10 across marine, freshwater, and terrestrial environments. **C)** lnCVR Q10 across traits for marine, freshwater and terrestrial systems. Note there were no differences between acute and acclimation Q10 types. k = total number of effect size estimates while the numbers in brackets indicate the number of species."}

@@

One explanation for why terrestrial ectotherms show minimal acclimation capacity may be related to the fact that terrestrial ectotherms, were, on average acclimated for significantly less time than ectotherms from aquatic habitats . Rates of acclimation have been shown to be faster for many terrestrial groups compared to aquatic organisms [e.g., amphibians and reptiles have higher rates of acclimation than fishes; See @Einum2023]. However, faster rates of acclimation would result in opposite patterns to those we observed -- in other words, terrestrial species would be more likely to exhibit lower $lnRR_{Q_{10}}_{acclimation}$ compared to $lnRR_{Q_{10}}_{acute}$ when controlling for acclimation time.

## References
<br>
<div id="refs"></div>
<br>

## Supplemental Results and Figures
